### 2024-10-10 project3/draft.tex
new

In our TL setting, both the source and target tasks involve learning a mapping from the risk factors to the VA contract losses.
For the source task, we have a dataset $\mathcal{D}_{\text{So}} = { (X_{\text{So}}^{(i)}, L_{\text{So}}^{(i)}) }{i=1}^{M_{\text{So}}}$, where $M_{\text{So}}$ is the number of training samples, i.e., the number of outer simulation paths used to generate the dataset with a standard nested simulation procedure.
$X_{\text{So}}^{(i)} \in \mathcal{X}_{\text{So}}$ and $L_{\text{So}}^{(i)} \in \mathcal{Y}_{\text{So}}$.

@@

In this section, we evaluate the performance of the TL framework for rapid adaptation of LSTM metamodels in dynamic hedging of VAs.
The low noise dataset generated by the standard nested simulation procedure in Section~\ref{sec2:numerical} is used to train the source LSTM metamodels.
We consider two target tasks: one with the same contract but different underlying asset model and another with different contracts but the same asset model.

Serveral datasets generated by related standard nested simulation procedures are considered as source and target tasks.
VA contract losses are simulated under geometric Brownian motion (GBM) and regime-switching GBM (RS-GBM) asset models.
The contracts include GMMB and GMWB contracts with no lapse, static lapse, and dynamic lapse features.
The source dataset is generated by running the standard nested simulation procedure for 50,000 VA contracts, while each target task consists of 2,000 new sample paths.

\begin{enumerate}
    \item   GMMB contracts under RS-GBM asset model with no lapse.
    \item   GMMB contracts under RS-GBM asset model with static lapse.
    \item   GMMB contracts under RS-GBM asset model with dynamic lapse.
    \item   GMWB contracts under RS-GBM asset model with dynamic lapse.
\end{enumerate}

From the first task to the last task, the complexity of the simulation schemes increases, and the LSTM metamodels need to adapt to the new conditions.
Similar to Chapter~\ref{chap:project2}, the true contract losses for all scenarios are approximated by the standard nested simulation procedures with 100,000 inner replications. 
The training datasets are generated on the same scenarios with 100 inner replications.
These datasets are referred to as the \textbf{true dataset} and the \textbf{training dataset}, respectively in Section~\ref{sec2:numerical}.
Hyperparameters, dropout rates, and network architectures for the LSTM metamodels are the same as the LSTM metamodel in Section~\ref{sec2:numerical}. 
Due to limited computational resources, macro replications are not feasible for the tranfer learning experiments.

\subsection{Fine-Tuning and Layer Freezing}

@@

We first compare the performance of fine-tuning and layer freezing on the target tasks.
Figure~\ref{fig3:figure1} compares the performance of LSTM metamodels on the target tasks with and without TL.
The learning history of the LSTM metamodels is shown for the target task of metamodeling GMMB contract losses on RS-GBM with static lapse.
The source task is GMMB contracts on RS-GBM with no lapse, and the target task is the same simulation scheme but with static lapse.
Figure~\ref{subfig3-1:extensive} demonstrates the performance of the LSTM metamodel trained extensively on the target task using $M_{\text{TA}} = 50,\!000$ samples, which serves as the benchmark for this study. 
The metamodel achieves a low validation error due to the availability of a large dataset.
In contrast, Figure~\ref{subfig3-1:without} presents the results of training without TL, where $M_{\text{So}} = 50,\!000$, and $M_{\text{TA}} = 2,\!000$ samples.
This approach leads to highly unstable training dynamics, with substantial fluctuations in the validation error.
Learning without transfer leads poor generalization and extreme overfitting. 
Often, the training data is limited for a new VA contract, and such instability is particularly problematic for quick adaptation of LSTM metamodels.
Figure~\ref{subfig3-1:fineTuning} shows the results of fine-tuning a pretrained metamodel on RS-GBM with no lapse.
Fine-tuning offers noticeable improvements over training without TL by reducing the instability and lowering the validation error. 
However, despite these improvements, fine-tuning may not fully mitigate the challenges of training with a small dataset.
The fine-tuned metamodel still exhibits some fluctuations in the validation error, indicating that the model may not generalize well to new conditions.
Figure~\ref{subfig3-1:layerFreezing} presents the results of layer freezing on the same target task.
Layer freezing offers a more stable training process compared to fine-tuning, with a lower validation error and reduced fluctuations during its training.
The underlying reason is that the LSTM layers are critical for capturing general feature representations that are transferable across tasks, and freezing these layers helps prevent overfitting to the target task.
Layer freezing effectively retains useful information from the source task, while allowing the model to adapt to the new conditions in a data-efficient manner.

@@

Figure~\ref{fig3:figure3} continues the investigation of layer freezing in the task of metamodeling GMMB contract losses on RS-GBM with dynamic lapse. 
When transferring knowledge from the GMMB model with static lapse, the primary adaptation for the target task involves learning the impact of dynamic lapse.
Freezing the LSTM layers and fine-tuning only the fully connected layer results in a higher validation error, which suggests a tendency of overfitting.
This indicates that the fully connected layer struggles to adapt to the changes in the temporal dynamics introduced by dynamic lapse.
In contrast, freezing the fully connected layer and fine-tuning the LSTM layers leads to a lower validation error and better generalization. 
This can be attributed to the fact that the LSTM layers are responsible for capturing the temporal dependencies associated with dynamic lapse, while the fully connected layer remains less sensitive to shifts in the financial time series.

This experiment emphasizes the importance of choosing which layers to freeze based on the nature of the source and target tasks. 
In this case, the temporal structure of the data requires the LSTM layers to be flexible in learning new patterns related to dynamic lapse, while the fully connected layer can retain its original functionality.

\subsection{Transfer Knowledge to Other Contract Types}

When transferring knowledge from one VA contract type to another, the LSTM metamodel needs to adapt to different contract features and time series dynamics.
We consider the task of metamodeling GMWB contract losses on RS-GBM with dynamic lapse, with the source tasks being GMMB contracts on RS-GBM also with dynamic lapse.
Figure~\ref{fig3:figure4} illustrates the learning curves of the LSTM metamodels fine-tuned from the GMMB contracts to the GMWB contracts.

@@

Figure~\ref{subfig3-4:extensive} presents the performance of an extensively trained LSTM metamodel on the target task using 50,000 samples, serving as a benchmark of best metamodel performance. 
The extensively trained metamodel achieves a low validation error and demonstrates stable convergence due to having enough training samples. 
In contrast, Figure~\ref{subfig3-4:without} shows the results of training the metamodel on the target task without TL, using only $M_{\text{TA}} = 2,\!000$ samples. The limited data leads to unstable training dynamics, with significant fluctuations in the validation error, indicating poor generalization and a tendency to overfit.

When applying fine-tuning from the GMMB source task, as depicted in Figure~\ref{subfig3-4:fineTuning}, the metamodel exhibits improved performance compared to training without TL. 
Fine-tuning results in a lower validation error and more stable convergence. 
Despite the differences between GMMB and GMWB contracts, there is still valuable information that can be transferred. 
Both the LSTM layers and the fully connected layers capture general temporal patterns and feature representations that are beneficial for the target task. 
Fine-tuning allows the metamodel to adjust all layers, facilitating better adaptation to the complexities introduced by the GMWB contracts.

However, when employing layer freezing, as shown in Figure~\ref{subfig3-4:layerFreezing}, the metamodel's performance deteriorates.
Freezing the layers trained on the GMMB contracts does not allow the metamodel to sufficiently adapt to the complexities of the GMWB contracts. 
The GMWB contracts are inherently more complex than GMMB contracts due to the guaranteed withdrawal benefits at each time step.
The complexity introduce significant changes in the time series dynamics that the metamodel needs to capture.
Freezing the LSTM layers or the fully connected layer hinders the metamodel's ability to learn these new patterns, and it leads to poor generalization and unstable error curves.

The failure of layer freezing in this context indicates that the difference between the source and target tasks is too substantial for this method to be effective. 
While layer freezing can be advantageous when the source and target tasks are closely related, it may hinder performance when the tasks diverge significantly.
In such circumstances, fine-tuning provides a better approach by allowing the metamodel to leverage transferable knowledge while adapting to the new task's specific requirements. 
Fine-tuning enables both the LSTM and fully connected layers to update their weights, capturing the complex dynamics of the GMWB contracts more effectively.

\begin{table}[ht!]
    \centering
    \begin{tabular}{lllll}
    \toprule
    \textbf{Source} & \textbf{Extensive} & \textbf{Fine-tuning} & \textbf{Layer Freezing} & \textbf{Without TL} \\
    \midrule
    No Lapse & N/A & 0.4894 & 0.3361 & N/A \\
    Static Lapse & N/A & 0.0794 & 0.0763 & N/A \\
    Dynamic Lapse & 0.0587 &  N/A &  N/A & 0.2950 \\
    \bottomrule
    \end{tabular}
    \caption{Comparison of different TL methods across various source tasks.}
    \label{tab3:transfer_learning_results}
\end{table}

Table~\ref{tab3:transfer_learning_results} summarizes the true MSEs of the LSTM metamodels trained using different TL methods across various source tasks.
The calculations are based on the metamodel predictions and the approximate true contract losses with $100,\!000$ inner replications.
The last row shows the performance of training without TL on the target task.
The results demonstrate the effectiveness of fine-tuning and layer freezing in transferring knowledge from different source tasks to the target task, and it is consistent with the observations from the learning curves.
These numerical results highlight the importance of selecting appropriate TL strategies based on the similarity between the source and target tasks. 
Even when the source and target contracts are substantially different, TL via fine-tuning can still offer performance improvements over training from scratch. 
The ability to transfer general feature representations underscores the value of TL in dynamic hedging of VAs. 
It enables more efficient training of metamodels and reduces computational burden for hedging new VA products. 
Therefore, it is still worthwhile to transfer information from GMMB contracts when developing metamodels for more complex VA contracts with limited simulation data.

@@

Multi-task learning enables the LSTM metamodels to learn shared representations across related VA contracts.
In this section, we examine the performance of multitask learning applied to two types of VAs, GMMB and GMWB with dynamic lapse rates.
The simulation datasets contrain $2,\!000$ samples for each contract type, and the LSTM metamodels are trained using multi-task learning. 
The metamodels are simultaneously trained to minimize the multi-task MSE loss function in Equation~\ref{eq3:multiTaskLoss}.
We use individual task training as a baseline for comparison, where the LSTM metamodels are trained separately on the GMMB and GMWB contracts.
The objective is to assess how multitask learning can improve the training efficiency and performance of both products compared to individual task training.

@@

Figure~\ref{fig3:figure5} comopares the learning curves for the training of GMMB and GMWB, with and without multitask learning.
The comparison between multitask learning (Figure~\ref{subfig3-5:multiTask} and~\ref{subfig3-5:fineTuning}) and individual task training ((Figure~\ref{subfig3-5:gmmb_individual} and~\ref{subfig3-5:gmwb_individual})) demonstrates the benefit of multi-task learning for both products. 
In the case of GMMB, multitask learning allows the model to achieve faster convergence while reducing overfitting.
For GMWB, the multi-task learning framework helps to stablize the training process.
The shared LSTM layers in the multitask model are able to capture common temporal patterns and dynamics, which benefits both GMMB and GMWB when training samples is scarce.
Similar to pooling in Chapter~\ref{chap:project1} but on a higher level, multi-task learning enables the LSTM metamodels to leverage shared representations across related VA contracts.

@@

Multi-task learning offers a robust framework for transferring knowledge across related simulation schemes in LSTM metamodeling for nested simulations. 
By sharing representations through the LSTM layers, the model can learn more generalizable features, enhancing performance on tasks with limited data. 
Careful selection of simulation schemes and thoughtful design of the network architecture are essential to maximize the benefits of MTL while mitigating potential challenges.

>>>>

In our TL setting, both the source and target tasks involve learning a mapping from the risk factors to the VA contract losses.
For the source task, we have a dataset $\mathcal{D}_{\text{So}} = { (X_{\text{So}}^{(i)}, L_{\text{So}}^{(i)}) }_{i=1}^{M_{\text{So}}}$, where $M_{\text{So}}$ is the number of training samples, i.e., the number of outer simulation paths used to generate the dataset with a standard nested simulation procedure.
$X_{\text{So}}^{(i)} \in \mathcal{X}_{\text{So}}$ and $L_{\text{So}}^{(i)} \in \mathcal{Y}_{\text{So}}$.

@@

In this section, we evaluate the performance of the TL framework for rapid adaptation of LSTM metamodels in dynamic hedging of VAs.
The low noise dataset generated by the standard nested simulation procedure in Section~\ref{sec2:numerical} is used to train the source LSTM metamodels.
We consider TL to two types of target tasks: (1) the same contract but different underlying asset model, and (2) different contracts but the same asset model.
Similar to Section~\ref{sec2:numerical}, we use the standard nested simulation procedure to generate the dataset for the source and target tasks.
Serveral VA datasets generated with the standard nested simulation procedures under geometric Brownian motion (GBM) and regime-switching GBM (RS-GBM) asset models.

\begin{table}[ht!] 
    \centering
    \begin{tabular}{lcccc} 
    \toprule
    \textbf{Contract} & \textbf{Asset Model} & \textbf{Lapse} & \textbf{$M_{\text{So}}$}  & \textbf{$M_{\text{Ta}}$}\\
    \midrule
    GMMB & GBM & No lapse & 50,000 & N/A \\
    GMMB & RS-GBM & No lapse & 50,000 & 2,000 \\
    GMMB & RS-GBM & Static lapse & 50,000 & 2,000 \\
    GMMB & RS-GBM & Dynamic lapse & 50,000 & 2,000 \\
    GMWB & RS-GBM & Dynamic lapse & N/A & 2,000 \\
    \bottomrule
    \end{tabular}
    \caption{VA Contracts for Transfer Learning Experiments}
    \label{tab3:contracts}
\end{table}

Table~\ref{tab3:contracts} lists the VA contracts used in the TL experiments.
These contracts include GMMB and GMWB contracts with no lapse, static lapse, and dynamic lapse features.
Before transferred to the target task, a LSTM metamodel is trained on a source dataset with $M_{\text{So}} = 50,\!000$ samples generated with $N_{\text{So}} = 100$ inner replications\footnotemark.
\footnotetext{The GMMB contract on the GBM asset model is an exception, where scenario-wise contract losses can be computed analytically.}
The pre-trained LSTM metamodel is then adapted to a target task that is different from the source task.
The training dataset for the target task has $M_{\text{Ta}} = 2,\!000$ samples generated with $N_{\text{Ta}} = 100$ inner replications.
During the training on both the source and target tasks, $10\%$ of the data is split into a validation dataset to monitor the training process and prevent overfitting using early stopping.
The complexity of the simulation schemes increases from the first task to the last task, and the LSTM metamodels need to adapt to the new conditions with limited training data on the target tasks.

All LSTM metamodels are evaluated based on their training history graphs for the target task, which plot training and validation MSE against the number of training epochs.
The training history graphs visualize the learning curves of the LSTM metamodels, which provide insights into stability and convergence behavior the metamodels.
We measure the generalization performance of the LSTM metamodels using the true MSE, which quantifies the accuracy of the LSTM metamodels in approximating the true inner simulation model of VA contracts.
The true MSE is computed by comparing the metamodel predictions with the true contract losses, which are approximated by the standard nested simulation procedure with $100,\!000$ inner replications.
Hyperparameters and network architectures for the LSTM metamodels are kept the same as the LSTM metamodel in Section~\ref{sec2:numerical}. 
Due to limited computational resources, macro replications are not feasible for the TL experiments.

\subsection{Learning Lapse Features}

@@

We first examine the performance of fine-tuning and layer freezing in adapting LSTM metamodels to new VA contracts with lapse features.
Figure~\ref{fig3:figure1} compares the performance of LSTM metamodels on the target tasks with and without TL.
Learning histories of the LSTM metamodels is shown for the target task of metamodeling GMMB contract losses on the RS-GBM asset model with static lapse.
The source task is hedging a GMMB contract on RS-GBM with no lapse, and the target task is hedging the same GMMB contract but with static lapse.
The simulation data for the target task is generated with the same nested simulation simulation procedure as the source task, except for the lapse feature.
Figure~\ref{subfig3-1:extensive} demonstrates the performance of the LSTM metamodel trained extensively only on the target task using $M_{\text{TA}} = 50,\!000$ samples, which serves as a benchmark for this study. 
The metamodel achieves a low validation MSE due to the availability of a large dataset.
In contrast, Figure~\ref{subfig3-1:without} presents the results of training directly on the target task without pre-training on the source task.
With $M_{\text{TA}} = 2,\!000$ samples, the LSTM metamodel struggles to learn the temporal dependencies and patterns in the target task.
It leads to highly unstable training dynamics, with substantial fluctuations in the validation MSE.
Learning without knowledge transfer leads poor generalization and extreme overfitting. 
Often, the training data is limited for a new VA contract, and such instability is particularly problematic for quick adaptation of LSTM metamodels.
TL techniques like fine-tuning and layer freezing can help mitigate these challenges.
Figure~\ref{subfig3-1:fineTuning} shows the results of fine-tuning a pretrained metamodel on RS-GBM with no lapse.
Fine-tuning offers a noticeable improvement over training without TL by reducing the instability in the validation MSE. 
However, despite this improvement, fine-tuning may not fully mitigate the challenges of training with a small dataset.
The fine-tuned metamodel struggles to achieve a low validation MSE.
Lowering the learning rate does not help the fine-tuned metamodel converge, and the validation MSE remains high after increasing the number of training epochs.
It indicates that fine-tuning may not be sufficient for limited training data.
Figure~\ref{subfig3-1:layerFreezing} presents the performance of layer freezing on the same target task.
Layer freezing offers a more stable training process compared to fine-tuning, with a lower validation error and reduced fluctuations during its training.
The LSTM layers are critical for capturing general feature representations that are transferable across tasks, and freezing these layers helps prevent overfitting to the target task.
In addition, the layer freezing approch tunes fewer neural network parameters than crude fine-tuning.
It allows the transferred metamodelmodel to only focus on learning the lapse features without excessively adjusting the general temporal representations learned from the source task.
This reduction in trainable parameters also accelerates the convergence process, and it leads to a more stable and efficient training on the target task.

@@

Figure~\ref{fig3:figure3} continues the investigation of layer freezing in the task of metamodeling GMMB contract losses on RS-GBM with dynamic lapse. 
When transferring knowledge from the GMMB model with static lapse, the primary adaptation for the target task involves learning the impact of dynamic lapse.
Freezing the LSTM layers and fine-tuning only the fully connected layer results in a higher validation error, which suggests a tendency of overfitting.
This indicates that the fully connected layer struggles to adapt to the changes in the temporal dynamics introduced by dynamic lapse, which can be viewed as another source of randomness in the time series.
In contrast, freezing the fully connected layer and fine-tuning the LSTM layers leads to a lower validation error and better generalization. 
This can be attributed to the fact that the LSTM layers are responsible for capturing the temporal dependencies associated with dynamic lapse, and the fully connected layer predicts the contract losses based on these learned features.

This experiment emphasizes the importance of choosing which layers to freeze based on the nature of the source and target tasks. 
In the case of learning dynamic lapse features, freezing the LSTM layers is not beneficial as they need to adapt to the new temporal patterns.

\begin{table}[ht!]
    \centering
    \begin{tabular}{lllll}
    \toprule
    \textbf{Source} & \textbf{Extensive} & \textbf{Fine-tuning} & \textbf{Layer Freezing} & \textbf{Without TL} \\
    \midrule
    No Lapse GMMB & N/A & 0.4894 & 0.3361 & N/A \\
    Static Lapse GMMB & N/A & 0.0794 & 0.0763 & N/A \\
    Dynamic Lapse GMMB & 0.0587 &  N/A &  N/A & 0.2950 \\
    \bottomrule
    \end{tabular}
    \caption{Comparison of different TL methods on GMMB contracts}
    \label{tab3:transfer_learning_results}
\end{table}

Table~\ref{tab3:transfer_learning_results} summarizes the true MSEs of the LSTM metamodels trained using different TL methods across various source tasks.
The calculations are based on the metamodel predictions and the true contract losses approximated with $100,\!000$ inner replications.
The first two rows show the performance of transferring knowledge from GMMB contracts with no lapse and static lapse to the target task of GMMB with dynamic lapse.
The last row shows the performance of training without TL on the target task.
The results demonstrate the effectiveness of fine-tuning and layer freezing in transferring knowledge from a related source tasks to the target task. 
When transferring from a source task with static lapse to a target task with dynamic lapse, the MSEs achieved are $0.0794$ for fine-tuning and $0.0763$ for layer freezing.
The benchmark MSE of $0.0587$, obtained from extensive training on the GMMB dynamic lapse task with much more samples.
While TL from static lapse GMMB do not reach this level of accuracy due to the limited data in the target task, they significantly outperform training without TL. 
This indicates that the models pre-trained on a static lapse setting are effective in capturing relevant features that are transferable to the dynamic lapse scenario.

However, when the source task is less similar to the target task, the benefits of TL are less pronounced. The MSEs in this case are higher, with fine-tuning resulting in $0.4894$ and layer freezing achieving $0.3361$. 
This suggests that the divergence between the source and target tasks can lead to negative transfer.
These results highlight the importance of selecting source tasks that share significant similarities with the target task to maximize the effectiveness of TL. 
When the source and target contracts are substantially different, the pre-trained metamodels may struggle to adapt to the new conditions, as they may not have learned features relevant to the target task.

\subsection{Transfer Knowledge to other Contract Types}

When transferring knowledge from one VA contract type to another, the LSTM metamodel needs to adapt to different contract features and time series dynamics.
We consider the task of metamodeling GMWB contract losses on RS-GBM asset model with dynamic lapse, with the source tasks being a GMMB contract on RS-GBM also with dynamic lapse.
Figure~\ref{fig3:figure4} illustrates the learning history of transferring pre-trained LSTM metamodels from the GMMB contracts to the GMWB contracts.

@@

Figure~\ref{subfig3-4:extensive} presents the performance of an extensively trained LSTM metamodel on the target task using 50,000 samples, serving as a benchmark of best metamodel performance. 
The extensively trained metamodel achieves a low validation error and demonstrates stable convergence due to having enough training samples. 
In contrast, Figure~\ref{subfig3-4:without} shows the results of training the metamodel directly on the target task with $2,\!000$ training samples. 
Fewer training samples and no prior knowledge leads to unstable training dynamics. 
The validation MSE fluctuates significantly.

When applying fine-tuning from the GMMB source task (Figure~\ref{subfig3-4:fineTuning}), the metamodel exhibits improved performance compared to training without TL. 
Fine-tuning results in a lower validation error and more stable convergence.
Despite the differences between GMMB and GMWB contracts, there is still valuable information that can be transferred. 
Both the LSTM layers and the fully connected layers capture general temporal patterns and feature representations that are beneficial for the target task. 
Fine-tuning allows the metamodel to adjust all its neural network layers. 
It allows better adaptation to the complexities introduced by the GMWB contract.

However, when employing layer freezing (Figure~\ref{subfig3-4:layerFreezing}), the metamodel's performance deteriorates.
Freezing some layers trained on the GMMB contracts does not allow the metamodel to sufficiently adapt to the complexities of the GMWB contracts. 
The GMWB contracts are inherently more complex than GMMB contracts due to the guaranteed withdrawal benefits at each time step, and the contract features are significantly different.
The complexity introduce significant changes in the time series dynamics that the metamodel needs to capture.
Freezing the LSTM layers or the fully connected layer hinders the metamodel's ability to learn these new patterns, and it leads to poor generalization and unstable error curves.

\begin{table}[ht!]
    \centering
    \begin{tabular}{lrr}
        \toprule
        \textbf{Model} & \textbf{Training MSE} & \textbf{True MSE} \\
        \midrule
        Without TL & 0.3588 & 0.4188 \\
        Fine Tuning & 0.1690 & 0.1780 \\
        Layer Freezing & 0.1828 & 0.2295 \\
        Extensive Training & 0.0853 & 0.0726 \\
        \bottomrule
    \end{tabular}
    \caption{Comparison of different TL methods on GMWB contracts}
    \label{tab3:transfer_learning_results_gmwb}
\end{table}

Table~\ref{tab3:transfer_learning_results_gmwb} summarizes the true MSEs of the LSTM metamodels on the GMWB contracts.
The suboptimal performance of layer freezing in this context indicates that the difference between the source and target tasks is too substantial for this method to be effective. 
While layer freezing can be advantageous when the source and target tasks are closely related, it may hinder performance when the tasks diverge significantly.
In such circumstances, fine-tuning provides a better approach by allowing the metamodel to leverage transferable knowledge while adapting to the new task's specific requirements. 
Fine-tuning enables both the LSTM and fully connected layers to update their weights, capturing the complex dynamics of the GMWB contracts more effectively.
This is particularly beneficial when developing metamodels for complex VA contracts with limited simulation data. 
For instance, transferring information from GMMB contracts can still be valuable when modeling GMWB contracts.
Both contracts share some common contract features and temporal patterns, which allows a pre-trained LSTM metamodel to capture generalizable features that provide a solid foundation for the target task.

@@

Multi-task learning enables the LSTM metamodels to learn shared representations across related VA contracts.
In this section, we examine the performance of multitask learning applied to two types of VAs, GMMB and GMWB with dynamic lapse rates.
The simulation datasets contrain $2,\!000$ samples for each contract type, and the LSTM metamodels are trained using multi-task learning. 
In our experiments, Algorithm~\ref{alg3:multiTaskLearning} is used to train the LSTM metamodels simultaneously to minimize the multi-task MSE loss function in Equation~\ref{eq3:multiTaskLoss}.
We use individual task training as a baseline for comparison, where the LSTM metamodels are trained separately on the GMMB and GMWB contracts.
The objective is to assess how multitask learning can improve the training efficiency and performance of both products compared to individual task training.

@@

Figure~\ref{fig3:figure5} compares the learning curves for the training of GMMB and GMWB, with and without multitask learning.
The comparison between multitask learning (Figure~\ref{subfig3-5:multiTask} and~\ref{subfig3-5:fineTuning}) and individual task training ((Figure~\ref{subfig3-5:gmmb_individual} and~\ref{subfig3-5:gmwb_individual})) demonstrates the benefit of multi-task learning for both products. 
In the case of GMMB, multitask learning allows the model to achieve faster convergence while reducing overfitting.
For GMWB, the multi-task learning framework helps to stablize the training process.
The shared LSTM layers in the multitask model are able to capture common temporal patterns and dynamics, which benefits both GMMB and GMWB when training samples is scarce.
Similar to pooling in Chapter~\ref{chap:project1} but on a higher level, multi-task learning enables the LSTM metamodels to leverage shared representations across related VA contracts.

% \begin{figure}[ht!]
%     \centering
%     \begin{subfigure}{0.48\textwidth}
%         \includegraphics[width=\textwidth]{./project3/figures/figure5a.png}
%         \caption{Multi-task training history} 
%         \label{subfig3-6:multiTask}
%     \end{subfigure}\hfill
%     \begin{subfigure}{0.48\textwidth}
%         \includegraphics[width=\textwidth]{./project3/figures/figure5b.png}
%         \caption{Task performance with multitask training}
%         \label{subfig3-6:fineTuning}
%     \end{subfigure}    
%     \label{fig3:figure6}
% \end{figure}

Even when data is abundant, multi-task learning can improve the training efficiency and predictive performance of LSTM metamodels for nested simulations.
The shared LSTM layers learn generalizable features that are beneficial across different VA contracts.
% Figure~\ref{fig3:figure6} demonstrates the performance of multi-task learning on GMMB and GMWB contracts with dynamic lapse rates.

@@

In this chapter, we introduced a transfer learning framework to accelerate the training of LSTM metamodels for dynamic hedging of variable annuity contracts.
Traditional nested simulation procedures for VA risk management are computationally intensive.
LSTM metamodels offer a data-driven approach to approximate the true contract losses, which can significantly reduce the computational cost of hedging a single VA contract.
However, training LSTM metamodels on new VA contracts can be challenging due to the limited availability of simulation data.
Our proposed framework leverages pre-trained LSTM networks and transfer learning techniques to adapt quickly metamodels to new but related VA contracts with minimal additional simulation cost.
Fine-tuning a pre-trained LSTM metamodel on a new target task with limited data significantly improved training stability and predictive accuracy compared to training from scratch. 
Layer freezing further enhanced performance by retaining transferable temporal representations learned from the source task. 
However, the success of these methods depends on the similarity between the source and target tasks. 
When the tasks were closely related, freezing some neural network layers yields substantial benefits. 
Conversely, when the source and target tasks diverged significantly, fine-tuning the entire network is more effective.

Multi-task learning offers a robust framework for transferring knowledge across related simulation schemes in LSTM metamodeling for nested simulations. 
By sharing representations through the LSTM layers, the model can learn more generalizable features that are beneficial across different VA contracts. 
The multi-task approach was particularly beneficial when training data for individual tasks was scarce, as it effectively pooled information across tasks to enhance learning efficiency and predictive performance.
Furthermore, a metamodel trained with multi-task learning can serve as a pre-trained model. 
It is adaptable to various VA contracts and asset models, and it is a versatile tool for practical applications in dynamic hedging of VAs.

The integration of transfer learning into LSTM metamodeling represents a significant advancement in robust risk management associated with variable annuity contracts.
By effectively leveraging existing knowledge, financial institutions can maintain accurate and responsive risk management practices in a rapidly changing market environment. 
The methodologies presented in this chapter not only contribute to the field of actuarial science but also open the door for broader applications of transfer learning in financial modeling and risk assessment.
